Foreground Detection via Deep Variation Transformation

### 2018-11-15 draft.tex
.

\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyze the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
In particular, the pixel variation is represented by the sequence of pixel observations, which is used as the input of fully convolutional network to find a transformation of pixels' variation.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a liner classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
the proposed approach adaptively generates superior performances in diverse nature scenes.
%
Comprehensive experiments in several standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
%
\end{abstract}

@@

% 第二段重点阐述什么是deep variation learning
% 在多样的自然场景中，前景可能产生和背景相似，甚至相同的像素，而这种像素很难去分析
In the diversely natural scenes,
it is possible that the moving objects produce the similar or even the same observations of pixels to that of background.
% similar to their counterparts of background but actually belong to foreground .
% 如图所示，像素观测值C就和背景的值几乎一模一样，
As shown in the \reffig{idea},
the observation C is closely related to the observations which belong to the background. However, it is actually produced by moving objects and should be classified as foreground.
% 大多数情况下，他都会被划分成背景
Unfortunately, in most cases, it is highly possible that the observation C will be falsely classified due to the similarity with their counterparts of background.
% 我们的就是希望把这个variation 转化到更简单的地方去
In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classified, rather than learning a classifier for individual pixels.
As shown in the bottom part of the \reffig{idea}, the pattern of fragment consist of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
% transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
Based on this motivation, the Deep Variation Transformation model for foreground detection is proposed.
% 
% %实际应用中的挑战
% \todo{the main purpose of the second paragraph is showing our idea. But be careful that you should not mention any details of our method which is the content of third paragraph. Pls re-write this part according to figure 1. The main content should be the description of figure 1, as well as our idea, insight}
% Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
% However, foreground detection is still unsolved because of the complexity and the diversity of natural scenes.
% There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}. In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
% To solve this problem, we bring up a novel conception of variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation. Each piece of pixel variation contains the complete temporal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
    \includegraphics[width=\linewidth]{figure/demo.pdf}
    % 图例里描述一下。
    \caption{The demonstration of deep variation transformation. Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly. After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
    \label{idea}
\end{figure}
%The demonstration of deep variation transformation. The pixels in the transformed variation become easier to be classified as foreground and background correctly
%本文的想法和优势
% The previous methods have already made great progress in generating some sophisticated background models with given videos. 
% Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them. 
% For instance, the statistical methods\cite{Stauffer1999} model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.

%具体介绍
% XXX 一句话，换一行！！！
% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for foreground detection in diversely natural scenes. 
In the DVTL model, 
the sequence of pixel observations is used to represent the variation and input into the network for learning,
which encode both the intensity distribution and sequential information.
%
Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantees the linear separability of pixels in the transformed variation.
%
In particular,
we take advantage of the strong learning ability of the deep neural network to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
%
Benefited from the novel framework of variation transformation,
proposed approach works well in diversely complex scenes adaptively.
%
%Moreover,
%since the pixel sequences are extracted from individual pixels, a large number of pixel patches may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
% 
% 
% 
% \todo{This paragraph is too short! provide comprehensive details of our work!}
% % The final prediction can be obtained by thresholding of the transformed variation. 
% %Our contributions can be summarized as follows:
% The contridbutions of proposed approach is shown as follows:
% \begin{itemize}
% \item We proposed the pixel observation patch to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
%     The observation patch is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
% \item We propose a deep neural network for variation transformation. 
%     Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
% \end{itemize}
% 
%文章结构

%The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. 
% XXX 不会用引用可以问我或者曲师兄。
The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion about the early and recent relevant works. 
%
The details of the variation transformation are presented in \refsec{sec3}. The architecture of network is introduced in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}. 
% \todo{please revise this part by using command refsec}

@@

%GMM 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods.
% 注意英语和汉语的表达习惯
It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
%GMM+i
Moreover,
Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of recursive equation
to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
The incoming pixels are compared with these codewords to see if their distances lies within a certain bound. 
%KDE
In addition, a non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
They assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
%Vibe
Another non-parametric method is proposed by Barnich et al. \cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). The background model of ViBe consists of pixel samples from the video stream. Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range. 
%PBAS
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold, which depended on the pixel position and a background dynamics metric.

%提出其他方法的问题，指出他们的缺陷
Unfortunately,
the pixel-based methods ignore the spatial-temporal information due to their assumption of independence between pixels.
But there is, in fact, a strong coherence in image sequences that contains abundant hidden clues for the background model. 
%
%提出我们的改进,我们认为像素在时序上是互相依赖的
% tight interdependence 明明在google scholar里查得到很多用的好不好...
% To address this shortcoming, 在一篇2018的CVPR的摘要里有啊
% “High Quality Estimation of Multiple Intermediate Frames for Video Interpolation”
To address this shortcoming, we introduce a framework of variation transformation learning, where pixel's historical observations are embedded in a piece of pixel patch and sorted in chronological order as a whole for the training of our DPVTL model.
%这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
Bringing together the historical observations ensures the data integrity and preserves the temporal coherence of our training data. 
On the other hand, the application of neural network guarantee the strong learning ability of our model.
Thus, the proposed approach is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers based on the assumption of pixel independence. 
%所以我们方法比基于像素的要好。
%Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
%\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
%
%
%
%
%
%
\subsection{region-based approach}
% Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
Region-based approaches consider the similarity between neighboring pixels, which is utilized to refine the pixel-level classification.
%

%(Regularized region-based)
Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
which is derived from expectation maximization theory with the consideration of neighboring pixels.
% Spatiotemporal GMM
In addition, 
Chen et al. \cite{2017_TPAMI_GANGWANG} combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
%(Bayesian Modeling)
Moreover, 
Sheikh et al.\ \cite{Sheikh2005Bayesian} introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
probability (MAP-MRF) estimation, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
%(Robust Foreground Object ICPR2010 Vikas Reddy )
% 这里原文就是用了三层的分类器，不同的方法，一层又一层。
Similarly, in \cite{Reddy2010Robust}, original images are divided into overlapping blocks. Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure and a temporal correlation check.
%( Robust Region-Based ICPR)
Hence, Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively. Any foreground region that does not exist in the first foreground map could be recovered from the other one.

In contrast, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, and combine the pixel variation with its spatial neighbors to revise our prediction. 
Due to the application of deep learning, the proposed approach is more powerful in capturing the structural background variation and achieves significant improvement compared to its competitors.
%
%
%
% \subsection{learning-based methods}
\subsection{Machine Learning based Methods}
The last category of background subtraction methods apply traditional machine learning and deep learning for the foreground detection.

@@

%
Recent years, deep learning methods start to flourish in several computer vision fields. A novel approach for foreground detection with the use of the Convolutional Neural Network(CNN) is proposed by Wang et al.\cite{wang2016PRL}.
They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently with sufficient training data.
%
% Ren: 这里我解释一下，为什么看上去这么冗余。这家伙先自己用中值滤波求了个平均背景，然后把平均背景 patches 跟对应的origin image patches 组合作为网络输入，他训练的groundtruth也可以来自其他比如GMM的分类结果图。
Braham et al. \cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth. In particular, the background image is obtained by temporal median filtering, and the groundtruth can be replaced with segmentation results from other foreground detection methods.
% Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
A similar approach is presented by M. Babaee et al. \cite{Babaee2017deep}. Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm \cite{Wang2014FTSG}, which is able to adaptively update the parameters used in the background model. They also utilize spatial-median filtering as the post processing of the network predictions.
%DBMF
In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed for foreground detection. 
The authors also proposed a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.

% cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
Some breakthroughs and progress have been achieved by applying those methods, especially deep learning based approaches with optimized network architectures. 
However, due to the diversity of nature scenes, pixel variations can be very complex, leading to difficulty in analyzing specific pixel variation patterns.
%我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
Unlike existing ones, our method focus on creating a transformation, which guarantees the linear separability of pixel variations in the mapping space, rather than building classifiers for individual observations.
%
Besides, our network is trained to learn the patterns of pixel variations, which promises a better performance in time series modeling on temporal coherence.
%
%Moreover, our DPVTL model is implemented without any assistance from other tradition foreground detection methods, hence the reliable performance owing to the novel framework of variation transformation.

@@

%背景检测的难点
foreground detection is essentially an binary classification in time sequence, where pixels in a video stream are classified as two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops). 
In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
However, there are some exceptions: historical observations varies regularly when belonging to some dynamic background scenes(e.g. 
waves, swaying tree leaves). 
Generally, pixels from the background are sharing some common patterns of variation. 
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
    \includegraphics[width=\linewidth]{figure/fig1}
    % 图例里描述一下。
    \caption{Comparison of the original pixel variation, groundtruth and transformed variation. They are represented by the blue line, red line and green line respectively.}
    \label{variation_chart}
\end{figure}
% It is hard to separate the foreground pixels from the background precisely in a time sequence.

%图例解释困难点
To give an intuitive understanding of the pixel variation, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}.
% with the X axis showing their range of variation and the Y axis representing the time. 
As we can see, there are several lines in three colors: blue, red and green. 
The blue line consist of original observations, representing a piece of pixel variation. 
Accordingly, the red line is made of the groundtruth data, corresponding to the observations from the blue one.  
And the green line consist of the outputs of the proposed approach which represent the transformed variation.

@@

%图例说明可能面临的挑战
For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
In that case, those popular methods will inevitably yield some sticky moments when separating the pixels in the blue line. 
Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations. 
In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, they still let the order information of sequential images all go to waste.

@@

Different from existing methods, we decide to shift our attention form single pixel classification to variation transformation.
%the pixel variation is now regarded as a whole to safeguard the data integrity.
More specifically, a FCN is employed to learn the patterns of pixel variations and mapping them into a new space where they are close to the groundtruth data.
The transformed variation is presented by the green line in \reffig{variation_chart}. 
%After thresholding, we can easily get the labels of each observation. 
%方法的好处是
The benefits are evident and clearly seen. 
It is hard to distinguish a foreground observation when its value are similar to the background ones. 
Classification on the transformed variation, however, is much more convenient and intuitive. 
With the strong learning ability of the FCN, we are able to learn the diverse variation patterns of background and foreground over a long period of time.
And the variation patterns, in turn, contribute to the variation transformation where the value of each observation is adjusted according to its compatriot in time sequence.

@@

%me
\section{foreground detection VIA DEEP VARIATION TRANSFORMATION}
\label{sec4}
In this section, we will introduce the details of proposed approaches. 
We explain the production of pixel patches, which is a specific form of the pixel variation, and the architecture of our network.

The flow chart of proposed approach is illustrated in \reffig{flow_chart}. 
Firstly, we sample the input and ground truth images to generalize the pixel variations, and reshape them into patches and feed them into the network with its spatial neighbors. 
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
\begin{figure*}[!t] % FIGURE: figure/fig1 
\centering
\includegraphics[width=\textwidth]{figure/fig2}
\DeclareGraphicsExtensions.
    \caption{ Original videos break down into pixel patches for the training of the FCN, which 
Fully convolutional network produces an efficient machine for end-to-end transformation learning.}
    \label{flow_chart}
\end{figure*}

>>>>

\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyze the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
In particular, the pixel variation is represented by the sequence of pixel observations, which is used as the input of fully convolutional network to find a transformation of pixels' variation.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a liner classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
the proposed approach adaptively generates superior performances in diverse nature scenes.
%
Comprehensive experiments in several standard benchmarks demonstrate the superiority of the proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
%
\end{abstract}

@@

% 第二段重点阐述什么是deep variation learning
% 在多样的自然场景中，前景可能产生和背景相似，甚至相同的像素，而这种像素很难去分析
In the diversely natural scenes,
it is possible that moving objects produce the similar or even the same observations of pixels to that of background.
% similar to their counterparts of background but actually belong to foreground .
% 如图所示，像素观测值C就和背景的值几乎一模一样，
As shown in the \reffig{idea},
the observation C is closely related to the observations which belong to the background. However, it is actually produced by moving objects and should be classified as foreground.
% 大多数情况下，他都会被划分成背景
Unfortunately, in most cases, it is highly possible that the observation C will be falsely classified due to the similarity with their counterparts of background.
% 我们的就是希望把这个variation 转化到更简单的地方去
In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classify, rather than learning a classifier for individual pixels.
As shown in the bottom part of the \reffig{idea}, the pattern of fragment consists of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
% transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
Based on this, the Deep Variation Transformation model for foreground detection is proposed.
% motivation
% %实际应用中的挑战
% \todo{the main purpose of the second paragraph is showing our idea. But be careful that you should not mention any details of our method which is the content of third paragraph. Pls re-write this part according to figure 1. The main content should be the description of figure 1, as well as our idea, insight}
% Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
% However, foreground detection is still unsolved because of the complexity and the diversity of natural scenes.
% There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}. In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
% To solve this problem, we bring up a novel conception of variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation. Each piece of pixel variation contains the complete temporal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
    \includegraphics[width=\linewidth]{figure/demo.pdf}
    % 图例里描述一下。
    \caption{The demonstration of deep variation transformation. Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly. After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
    \label{idea}
\end{figure}
%The demonstration of deep variation transformation. The pixels in the transformed variation become easier to be classified as foreground and background correctly
%本文的想法和优势
% The previous methods have already made great progress in generating some sophisticated background models with given videos. 
% Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them. 
% For instance, the statistical methods\cite{Stauffer1999} model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.

%具体介绍
% XXX 一句话，换一行！！！
% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for foreground detection in diversely natural scenes. 
In the DVTL model, 
the sequence of pixel observations is used to represent the variation and input into the network for learning,
which encode both the intensity distribution and sequential information.
%
Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn patterns of the pixel variation and find a transformation which guarantees the linear separability of pixels in the transformed variation.
%
In particular,
we take advantage of the strong learning ability of the deep neural network to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
%
Benefited from the innovative framework of variation transformation,
proposed approach works well in diversely complex scenes adaptively.
%
%Moreover,
%since the pixel sequences are extracted from individual pixels, a large number of pixel patches may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
% 
% 
% 
% \todo{This paragraph is too short! provide comprehensive details of our work!}
% % The final prediction can be obtained by thresholding of the transformed variation. 
% %Our contributions can be summarized as follows:
% The contridbutions of proposed approach is shown as follows:
% \begin{itemize}
% \item We proposed the pixel observation patch to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
%     The observation patch is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
% \item We propose a deep neural network for variation transformation. 
%     Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
% \end{itemize}
% 
%文章结构

%The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. 
% XXX 不会用引用可以问我或者曲师兄。
The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion of the early and recent relevant works. 
%
The details of the variation transformation are presented in \refsec{sec3}. The architecture of network is introduced in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}. 
% \todo{please revise this part by using command refsec}

@@

%GMM 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods.
% 注意英语和汉语的表达习惯
It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
%GMM+i
Moreover,
Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of the recursive equation
to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
The incoming pixels are compared with these codewords to see if their distances lie within a certain bound. 
%KDE
In addition, a non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
They assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
%Vibe
Another non-parametric method is proposed by Barnich et al. \cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). The background model of ViBe consists of pixel samples from the video stream. Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exist sufficient samples with a distance to itself within a certain range. 
%PBAS
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold, which depended on the pixel position and a background dynamics metric.

%提出其他方法的问题，指出他们的缺陷
Unfortunately,
the pixel-based methods ignore the spatial-temporal information due to their assumption of independence between pixels.
But there is, in fact, a strong coherence in image sequences that contains abundant hidden clues for the background model. 
%
%提出我们的改进,我们认为像素在时序上是互相依赖的
% tight interdependence 明明在google scholar里查得到很多用的好不好...
% To address this shortcoming, 在一篇2018的CVPR的摘要里有啊
% “High Quality Estimation of Multiple Intermediate Frames for Video Interpolation”
To address this shortcoming, we introduce a framework of variation transformation learning, where pixel's historical observations are embedded in a piece of pixel patch and sorted in chronological order as a whole for the training of our DPVTL model.
%这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
Bringing together the historical observations ensures the data integrity and preserves the temporal coherence of our training data. 
On the other hand, the application of neural network guarantees the strong learning ability of our model.
Thus, the proposed approach is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers based on the assumption of pixel independence. 
%所以我们方法比基于像素的要好。
%Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
%\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
%
%
%
%
%
%
\subsection{region-based approach}
% Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
Region-based approaches consider the similarity between neighboring pixels, which is utilized to refine the pixel-level classification.
%

%(Regularized region-based)
Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
which is derived from expectation-maximization (EM) theory with the consideration of neighboring pixels.
% Spatiotemporal GMM
In addition, 
Chen et al. \cite{2017_TPAMI_GANGWANG} combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
%(Bayesian Modeling)
Moreover, 
Sheikh et al.\ \cite{Sheikh2005Bayesian} introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
probability (MAP-MRF) estimation, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
%(Robust Foreground Object ICPR2010 Vikas Reddy )
% 这里原文就是用了三层的分类器，不同的方法，一层又一层。
Similarly, in \cite{Reddy2010Robust}, original images are divided into overlapping blocks. Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure and a temporal correlation check.
%( Robust Region-Based ICPR)
Hence, Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively. Any foreground region that does not exist in the first foreground map could be recovered from the other one.

In contrast, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, and combine the pixel variation with its spatial neighbors to revise our prediction. 
Due to the application of deep learning, the proposed approach is more powerful in capturing the structural background variation and achieves significant improvement compared to its competitors.
%
%
%
% \subsection{learning-based methods}
\subsection{Machine Learning based Methods}
The last category of background subtraction methods applies traditional machine learning and deep learning for the foreground detection.

@@

%
Recent years, deep learning methods begin to flourish in several computer vision fields. A novel approach for foreground detection with the use of the Convolutional Neural Network(CNN) is proposed by Wang et al.\cite{wang2016PRL}.
They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which performs excellently with sufficient training data.
%
% Ren: 这里我解释一下，为什么看上去这么冗余。这家伙先自己用中值滤波求了个平均背景，然后把平均背景 patches 跟对应的origin image patches 组合作为网络输入，他训练的groundtruth也可以来自其他比如GMM的分类结果图。
Braham et al. \cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth. In particular, the background image is obtained by temporal median filtering, and the groundtruth can be replaced with segmentation results from other foreground detection methods.
% Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
A similar approach is presented by M. Babaee et al. \cite{Babaee2017deep}. Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm \cite{Wang2014FTSG}, which is able to adaptively update the parameters used in the background model. They also utilize spatial-median filtering as the post processing of the network predictions.
%DBMF
In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed. 
The authors also utilize a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.

% cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
Some breakthroughs and progress have been achieved by applying those methods, especially deep learning based approaches with optimized network architectures. 
However, due to the diversity of nature scenes, pixel variations can be very complex, leading to difficulty in analyzing specific pixel variation patterns.
%我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
Unlike existing ones, our method focus on creating a transformation, which guarantees the linear separability of pixel variations in the mapping space, rather than building classifiers for individual observations.
%
Besides, our network is trained to learn patterns of pixel variations, which promise a better performance in time series modeling on temporal coherence.
%
%Moreover, our DPVTL model is implemented without any assistance from other tradition foreground detection methods, hence the reliable performance owing to the novel framework of variation transformation.

@@

%背景检测的难点
Foreground detection is essentially a binary classification in time sequence, where pixels in a video stream are classified as two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops). 
In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
However, there are some exceptions: historical observations vary regularly when belonging to some dynamic background scenes(e.g. 
waves, swaying tree leaves). 
Generally, pixels from the background are sharing some common patterns of variation. 
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
    \includegraphics[width=\linewidth]{figure/fig1}
    % 图例里描述一下。
    \caption{Comparison of the original pixel variation, groundtruth and transformed variation. They are represented by the blue line, red line and green line respectively.}
    \label{variation_chart}
\end{figure}
% It is hard to separate the foreground pixels from the background precisely in a time sequence.

%图例解释困难点
To give an intuitive understanding of the pixel variation, we plot the historical observations and the corresponding groundtruth of a single pixel in  \reffig{variation_chart}.
% with the X axis showing their range of variation and the Y axis representing the time. 
As we can see, there are several lines in three colors: blue, red and green. 
The blue line consists of original observations, representing a piece of pixel variation. 
Accordingly, the red line is made of the groundtruth data, corresponding to the observations from the blue one.  
And the green line consists of the outputs of the proposed approach which represent the transformed variation.

@@

%图例说明可能面临的挑战
For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the same or similarly value with background ones. 
In that case, those popular methods will inevitably yield some sticky moments when separating the pixels in the blue line. 
Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations. 
In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, they still let the order information of sequential images all go to waste.

@@

Different from existing methods, we decide to shift our attention from single pixel classification to variation transformation.
%the pixel variation is now regarded as a whole to safeguard the data integrity.
More specifically, a FCN is employed to learn patterns of pixel variations and mapping them into a new space where they are close to the groundtruth data.
The transformed variation is presented by the green line in \reffig{variation_chart}. 
%After thresholding, we can easily get the labels of each observation. 
%方法的好处是
The benefits are evident and clearly seen. 
It is hard to distinguish a foreground observation when its value is similar to the background ones. 
Classification on the transformed variation, however, is much more convenient and intuitive. 
With the strong learning ability of the FCN, we are able to learn the diverse variation patterns of background and foreground over a long period of time.
And the variation patterns, in turn, contribute to the variation transformation where the value of each observation is adjusted according to its compatriot in time sequence.

@@

%me
\section{foreground detection VIA DEEP VARIATION TRANSFORMATION}
\label{sec4}
In this section, we will introduce the details of proposed approaches. 
We explain the production of the pixel patch, which is a specific form of the pixel variation, and the architecture of our network.

The flow chart of the proposed approach is illustrated in \reffig{flow_chart}. 
Firstly, we sample the input and ground truth images to generalize the pixel variations, and reshape them into patches and feed them into the network with its spatial neighbors. 
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
\begin{figure*}[!t] % FIGURE: figure/fig1 
\centering
\includegraphics[width=\textwidth]{figure/fig2}
\DeclareGraphicsExtensions.
    \caption{ Original videos break down into pixel patches for the training of the FCN, which 
Fully convolutional network produces an efficient machine for end-to-end transformation learning.}
    \label{flow_chart}
\end{figure*}
